Pool Model

### 2023-12-20 pool_model.tex
label subsection in supplement
update graphs and parameters to fit new simulation data

    \includegraphics[width=0.6\textwidth]{Figures/spatial_cell_growth.png}
    \includegraphics[width=0.5\textwidth]{Figures/lag_phase.png}%
    \includegraphics[width=0.5\textwidth]{Figures/entropy.png}
    % TODO difference to pool model
    \label{fig:spatial-lag-phase-entropy}

@@

        \dot{R^*} = -\frac{\alpha_A}{N_t} R^* G_A-\frac{\alpha_B}{(1 + \mu_I I) N_t} R^* G_B \\

@@

@@

@@

    \kappa &= b\\
    \alpha &= u\sigma\frac{1}{V_D}\\
    \mu_I &= \nu_I \frac{1}{V_D}

@@

    \includegraphics[width=0.6\textwidth]{Figures/pool_model_spatial.pdf}

@@

        The output of the model (\ref{eq:spatial_limit_F}, \ref{eq:spatial_limit_H}) for given parameters and initial valued presented in Tables \ref{tab:spatial_limit_param}, \ref{tab:spatial_limit_init}, respectively.
        The observables of the system are the bacterial count of each species $L+G$ (blue and orange lines) and the total bacterial count of the system (green).

@@

    \label{fig:spatial_limit_plot1}

@@

        Rate $L_A\rightarrow G_A$   & $\lambda_A$   & $0.001$\unit{\per\minute}
        &                           & $\lambda_A$   & $0.001$\unit{\per\minute}\\

@@

        Production $G_A$            & $\alpha_A$    & ??\unit{\per\minute}

@@

        Production $G_B$            & $\alpha_B$    & ??\unit{\per\minute}

@@

        Production $I$              & $\kappa$      & $1.18\cdot10^{-5}$\unit{\per\minute}

@@

        Inhibition         & $\mu_I$       & $1.11\cdot 10^{-6}$\unit{\per\micro\metre\cubed}

@@

        Total volume     & $N_t$         & $1.80\cdot 10^4$\unit{\micro\metre\cubed}

@@

        Volume of $L_A$             & $L_A$         & $35.34$\unit{\micro\metre\cubed}
        & Cell Number               & $C_A$         & 5\\

@@

        Volume of $L_B$             & $L_B$         & $28.27$\unit{\micro\metre\cubed}
        & Cell Number               & $C_B$         & 4\\

@@

        & Nutrients                 & $A$           & 2.0\unit{\mol\per\micro\metre\cubed}\\

@@

>>>>

@@

        \dot{R^*} = -\frac{\alpha_A}{G_\text{max}} R^* G_A-\frac{\alpha_B}{(1 + \mu_I I) G_\text{max}} R^* G_B \\

@@

Note that we do not need to distinguish between the two species because we can set parameters individually on agent-level.
This means, we can implement the most general version of the equations and by choosing appropriate parameters, set the species of the respective cell-agent.

@@

The derived equations read

@@

@@

and the \ac{ode} equations are
    \dot{L_A} &= -\lambda_A R^* L_A\\
    \dot{G_A} &= \lambda_A R^* L_A + \alpha_A R^* G_A\\
    \dot{L_B} &= -\lambda_B R^* L_B\\
    \dot{G_B} &= \lambda_B R^* L_B + \frac{\alpha_B}{1 + \mu_I I} R^* G_B\\
    \dot{R^*} &= -\frac{\alpha_A}{G_\text{max}} R^* G_A-\frac{\alpha_B}{(1 + \mu_I I) G_\text{max}} R^* G_B \\
    \dot{I} &= \kappa G_A
We compare the most general version and thus omit species $A$ for the moment.
\begin{table}
    \renewcommand{\arraystretch}{1.5}
    \begin{tabularx}{\textwidth}{@{}l *3{>{\centering\arraybackslash}X}@{}}
        & \textbf{\acs{ode}}
        & \textbf{\acs{abm}}
        & \textbf{Mappings}\\

        \multirow{2}{*}{Resource}
        & \multirow{2}{*}{$\displaystyle \dot{R^*} = - \frac{\alpha}{(1 + \mu_I I) G_\text{max}} R^* G$}
        & \multirow{2}{*}{$\displaystyle \dot{R} = -\frac{u}{1+\nu_I V_D^{-1}I} \frac{1}{V_D} R V$}
        & $\displaystyle G_\text{max} = [R_0] V_D \sigma$\\

        &&& $\displaystyle \mu_I = \frac{\nu_I}{V_D}$\\

        Volume
        & $\displaystyle \dot{G} = \frac{\alpha}{1 + \mu_I I} R^* G$
        & $\displaystyle \dot{V} = \frac{u}{1+\nu_I V_D^{-1} I} \frac{1}{V_D}\sigma R V$
        & $\displaystyle \alpha = u[R_0]\sigma$\\

        Inhibitor
        & $\displaystyle \dot{I} = \kappa G_A$
        & $\displaystyle \dot{I} = b V$
        & $\displaystyle \kappa = b$\\
We can use these mappings to numerically compare both approaches.
Table~\ref{tab:spatial_limit_init} shows a comparison of paramters of two simulations for the \ac{ode} and \ac{abm} model which have been mapped onto each other.
Figure~\ref{fig:spatial-snapshots} shows individual snapshots of different 
    \includegraphics[width=0.7\textwidth]{Figures/abm_ode_comparison.png}

@@

        Comparison of the \ac{abm} and \ac{ode} output corresponding to the parameters presented in table~\ref{tab:spatial_limit_init}.
        % TODO

@@

@@

        Rate $L_A\rightarrow G_A$   & $\lambda_A$   & $0.0025$\unit{\per\minute}
        &                           & $\lambda_A$   & $0.008$\unit{\per\minute}\\

@@

        Production $G_A$            & $\alpha_A$    & $0.002$\unit{\per\minute}

@@

        Production $G_B$            & $\alpha_B$    & $0.002$\unit{\per\minute}

@@

        Production $I$              & $\kappa$      & $0.1$\unit{\per\minute}

@@

        Inhibition         & $\mu_I$       & $1.0\cdot 10^{-7}$\unit{\per\micro\metre\cubed}

@@

        Total volume     & $G_\text{max}$         & $2.0\cdot 10^5$\unit{\micro\metre\cubed}

@@

        Volume of $L_A$             & $L_A$         & $127.2$\unit{\micro\metre\cubed}
        & Cell Number               & $C_A$         & 18\\

@@

        Volume of $L_B$             & $L_B$         & $127.23$\unit{\micro\metre\cubed}
        & Cell Number               & $C_B$         & 18\\

@@

        & Nutrients                 & $A$           & $1.0$\unit{\mol\per\micro\metre\cubed}\\

@@

\label{subsec:supplement-deriving-pool-odes}
